Informing forest carbon inventories under the Paris Agreement using the Global Forest Carbon Database (ForC v4.0)

### 2023-10-26 doc/manuscript/ForC-EFDB manuscript.Rmd
convert tables (now they show up)

```{r table_pools, eval = TRUE, echo=FALSE, warning=FALSE}
C_pools_table <- read.csv("figures_tables/C_pools.csv")
names(C_pools_table) <- stringr::str_replace_all(names(C_pools_table), "\\.", " ")

library(knitr)
library(kableExtra)
knitr::kable(C_pools_table, format = "latex",
             longtable = FALSE,
             caption = "\\textbf{IPCC-defined forest carbon pools with definitions and measurement methods.} Definitions from IPCC Table 1.1. (See Table 1.1 in IPCC guidance).") %>%
  row_spec(0, bold = TRUE) %>%
  kableExtra::kable_styling(full_width = TRUE) 
  #kable_styling(latex_options = c("scale_down", "hold_position"), protect_latex = T) 
```

@@

\newpage
```{r table_variables, eval = TRUE, echo=FALSE, warning=FALSE}
C_variables_table <- read.csv("figures_tables/C_variables.csv")
names(C_variables_table) <- stringr::str_replace_all(names(C_variables_table), "\\.", " ")
C_variables_table[is.na(C_variables_table)]<- "" #replace NAs with blanks

library(knitr)
library(kableExtra)
knitr::kable(C_variables_table[,-1], format = "latex",  
             longtable = T,
             caption = "\\textbf{Numbers of records of ForC variables (or closely related variable groups) relevant to, and sent to, EFDB.}") %>%
  row_spec(0, bold = TRUE)  %>%
  row_spec(which(C_variables_table$bold), bold = TRUE) %>% #total
  kable_styling(font_size = 8) %>%
  #kableExtra::kable_styling(full_width = TRUE) 
  kable_styling(latex_options = c("hold_position", "repeat_header"), protect_latex = T) 
```

@@

```{r table_recommendations, eval = TRUE, echo=FALSE, warning=FALSE}
recommendations_table <- read.csv("figures_tables/recommendations.csv")
names(recommendations_table) <- stringr::str_replace_all(names(recommendations_table), "\\.", " ")

library(knitr)
library(kableExtra)
knitr::kable(recommendations_table, format = "latex",
             longtable = FALSE,
             caption = "\\textbf{Recommended best practices for reporting forest C estimates of value to national greenhouse gas inventories under IPCC guidance.}") %>%
  row_spec(0, bold = TRUE)%>%
  kable_styling(font_size = 10) %>%
  kableExtra::kable_styling(full_width = TRUE) 
  #kable_styling(latex_options = c("scale_down", "hold_position"), protect_latex = T) 
```

>>>>

\newpage
**Table `r table_pools`. IPCC-defined forest carbon pools with definitions and measurement methods.** <!--Definitions from IPCC Table 1.1. (See Table 1.1 in IPCC guidance).-->
```{r table_pools, eval = TRUE, echo=FALSE, warning=FALSE}
C_pools_table <- read.csv("figures_tables/C_pools.csv")
names(C_pools_table) <- stringr::str_replace_all(names(C_pools_table), "\\.", " ")

library(flextable)
set_flextable_defaults(font.family = "Arial", font.size = 8) # set font

ft <- flextable(C_pools_table)
ft <- autofit(ft)
ft <- width(ft, 1, width = 1)
ft <- width(ft, 2:4, width = 2)
ft <- bold(ft, i = 1, j = NULL, bold = TRUE, part = "header") # put title in bold
ft
```

@@

\newpage
**Table `r table_variables`. Numbers of records of ForC variables (or closely related variable groups) relevant to, and sent to, EFDB.**
```{r table_variables, eval = TRUE, echo=FALSE, warning=FALSE}
C_variables_table <- read.csv("figures_tables/C_variables.csv")
names(C_variables_table) <- stringr::str_replace_all(names(C_variables_table), "\\.", " ")
C_variables_table[is.na(C_variables_table)]<- "" #replace NAs with blanks

library(flextable)
set_flextable_defaults(font.family = "Arial", font.size = 8) # set font

ft <- flextable(C_variables_table[,-1])
ft <- autofit(ft)
ft <- width(ft, 1, width = 2)
ft <- width(ft, 2:5, width = 1)
ft <- bold(ft, i = 1, j = NULL, bold = TRUE, part = "header") # put title in bold
ft <- bold(ft, i = which(C_variables_table$bold), j = NULL, bold = TRUE, part = "body") # put categories in bold
ft
```

@@

\newpage
**Table `r table_recommendations`. Recommended best practices for reporting forest C estimates of value to national greenhouse gas inventories under IPCC guidance.**
```{r table_recommendations, eval = TRUE, echo=FALSE, warning=FALSE}
recommendations_table <- read.csv("figures_tables/recommendations.csv")
names(recommendations_table) <- stringr::str_replace_all(names(recommendations_table), "\\.", " ")

library(flextable)
set_flextable_defaults(font.family = "Arial", font.size = 8) # set font

ft <- flextable(recommendations_table)
ft <- autofit(ft)
ft <- width(ft, 1, width = 1)
ft <- width(ft, 2:3, width = 3)
ft <- bold(ft, i = 1, j = NULL, bold = TRUE, part = "header") # put title in bold
ft
```
